---
title: Some code from Ariana 
author: "AS Huffmyer"
date: '2023'
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_depth: 6
    toc_float: yes
  pdf_document:
    keep_tex: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(car)
```

## Load some data 

Load some data for coral larval size in two temperature treatments. 
```{r}
data<-read_csv(file="data/11-ashuff-larval-size-data.csv")

data<-data%>%
  select(!volume.mm3)
```

Calculate volume as a prolate spheroid. 
```{r}
data<-data%>%
  mutate(volume.mm3=((4/3) * pi * (width.mm/2) * (length.mm/2)^2))
```

Look at the data. 
```{r}
str(data)
head(data)
```

## Run some code 

Filter data to only the final time point. 
```{r}
data<-data%>%
  filter(!timepoint=="Baseline")
```

Run anova model to look at treatment differences. 
```{r}
model<-aov(volume.mm3~treatment, data=data)

summary(model)
qqPlot(residuals(model))
```

Plot the data. 
```{r}
plot<-data %>%
    filter(timepoint=="Sampling")%>%
  
    ggplot(., aes(x = as.factor(treatment), y = volume.mm3)) +
    geom_boxplot(aes(color=treatment), outlier.shape=NA, lwd=0.5) +
    geom_point(aes(fill=treatment), pch = 21, size=4, position = position_jitterdodge(0.2), alpha=0.2) + 
    scale_fill_manual(values=c("blue", "red"))+
    scale_color_manual(values=c("blue", "red"))+
    xlab("") + 
    ylab(expression(bold(paste("Larval Size (mm"^3, ")"))))+
    geom_text(x=1.5, y=0.0, label="p<0.001", color="black", size=5)+
    theme_classic() + 
    ylim(0,0.12)+
    theme(
      legend.position="none",
      axis.title=element_text(face="bold", size=14),
      axis.text=element_text(size=12, color="black"), 
      legend.title=element_text(face="bold", size=14)
      ); plot
```


## Output some new data 

Generate a data frame that outputs descriptive statistics for larval size in each treatment. 
```{r}
data %>%
    filter(!timepoint=="Baseline")%>% #keep just the end time point
    group_by(treatment)%>%
    dplyr::summarise(mean=mean(volume.mm3, na.rm=TRUE), 
                     n=length(volume.mm3),
                     sd=sd(volume.mm3, na.rm=TRUE),
                     se=sd/sqrt(n))%>%
    write_csv("output/11-ashuff-output-data.csv")
```

